\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking} 
\moderncvcolor{black}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
% More styles for bullets
\usepackage{pifont}

\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}
% Personal data
\firstname{Nada}
\familyname{Alghamdi}
\address{Jeddah}{23235, Saudi Arabia}
\email{nada.ghamdi13@gmail.com}
\phone[mobile]{+966~504~587~342}
\social[linkedin]{nada-ghamdi} % Your LinkedIn username
\begin{document}
\setlength{\parskip}{10mm} % Adjust the 5mm to increase or decrease the space

\makecvtitle

\cvitem{}{A passionate physicist with a strong focus on computational materials science and condensed matter physics. Proficient in using Density-Functional Theory (DFT) for advanced research and analysis. Committed to contributing to groundbreaking research in these fields.}
\section{Education}
\cventry{Feb 2021--Aug 2023}{Master of Science MSc in Physics}{École polytechnique fédérale de Lausanne (EPFL)}{Lausanne, Switzerland}{}{
\begin{itemize}
    \item[\ding{169}] Physics major and Computational Science and Engineering minor. Graduated with 5.24 out of 6 GPA. 
    \item[\ding{169}] Full scholarship holder from The Custodian of The Two Holy Mosques Scholarship Program.
    \item[\ding{169}] Master’s thesis on the magnetic and electronic properties of mixed valence magnetite Fe$_3$O$_4$ using DFT+Hubbard corrections done in the group of Prof. Nicola Marzari.
\end{itemize} }
\vspace{4mm} % Adjust the 5mm as needed
\cventry{Sep 2015--May 2019}{Bachelor of Science B.Sc in Physics}{King Abdulaziz University}{Jeddah, Saudi Arabia (KSA)}{}{
\begin{itemize}
    \item[\ding{169}] Graduated with first class honors and 5 out of 5 GPA.
    \item[\ding{169}] Recipient of the University President's Prize for Scientific Excellence.
\end{itemize}}

\section{Research Experience}
\cventry{Sep 2019--Feb 2020}{Intern}{King Abdullah University of Science and Technology (KAUST)}{Thuwal, KSA}{}{ 
\begin{itemize}
    \item[\ding{169}] Conducted computational material science research using density functional theory (DFT) under the supervision of Prof. Udo Schwingenschlögl.
    \item[\ding{169}] Studied n-type conductivity in diamond by phosphorus doping and boron-phosphorus co-doping.
\end{itemize} }
\vspace{4mm} % Adjust the 5mm as needed
\cventry{Jul 2019--Aug 2019}{Summer Student}{The European Organization for Nuclear Research (CERN)}{Geneva, Switzerland}{}{
\begin{itemize}
    \item[\ding{169}] Worked in the tile calorimeter upgrade project in ATLAS experiment and attended high energy physics lectures.
    \item[\ding{169}] Prepared scintillators, conducted Sr-90 scans, and plotted the resulted graphs.
    \item[\ding{169}] Made a presentation and wrote a report at the end of the program.
\end{itemize} }
\vspace{4mm} % Adjust the 5mm as needed
\cventry{May 2018--Aug 2018}{Summer Intern}{King Abdullah University of Science and Technology (KAUST)}{Thuwal, KSA}{}{
\begin{itemize}
    \item[\ding{169}]Used Quantum Espresso and Wien2k (DFT codes) and participated in nanodiamond research project.
\end{itemize}}
\vspace{4mm} % Adjust the 5mm as needed
\cventry{Nov 2017--Oct 2018}{Participant in a Research Project}{King Abdulaziz University}{Jeddah, KSA}{}{
\begin{itemize}
    \item[\ding{169}] Evaluated the electrocatalytic activity of green synthesized CuO thin films. Measured current-voltage relation of the catalyst and plotted the resulted graphs.
\end{itemize}}
\vspace{4mm} % Adjust the 5mm as needed
\cventry{Sep 2014}{Summer Student}{Center for Talented Youth in Johns Hopkins University and Saudi Aramco}{Al-Dammam, KSA}{}{
\begin{itemize}
    \item[\ding{169}] Three weeks summer program for gifted high school students in Saudi Arabia, focusing on scientific literature and presentation.
\end{itemize}}

\section{Leadership Experience}
\cventry{May 2018--Jan 2019}{Volunteer Translator}{Jeddah, KSA}{}{}{
\begin{itemize}
    \item[\ding{169}] Translated one TEDx video and three TED-Ed videos to Arabic.
    \item[\ding{169}]  Translated two articles for the Scientific Saudi website.
\end{itemize}}
\vspace{4mm} % Adjust the 5mm as needed
\cventry{Sep 2017--Jan 2018}{Mentor}{King Abdulaziz University}{Jeddah, KSA}{}{
\begin{itemize}
    \item[\ding{169}] Gave supplementary lessons in the general physics course to help students improve their grades.
\end{itemize}}

\section{Research}
\cvitem{Published}{
\begin{itemize}
    \item[\ding{169}] N. Alhebshi, H. Huang, R. Ghandour, \textbf{N. Alghamdi}, et al. "Green Synthesized Cu$_x$O@Cu Nanocomposites on a Cu Mesh With Dual Catalytic Functions for Dye Degradation and Hydrogen Evaluation." \textit{Journal of Alloys and Compounds}.
\end{itemize}}
\cvitem{In prepration}{
\begin{itemize}
\item[\ding{169}] Electronic and magnetic properties of mixed valence magnetite Fe$_3$O$_4$ using DFT+Hubbard corrections. \textbf{N. Alghamdi}, E. Di Lucente, M. Cococcioni, N. Marzari.
\item[\ding{169}] P-Doping and B-P Co-Doping for n-Type Conductivity in Diamond. \textbf{N. Alghamdi}, U. Schwingenschlögl.
\end{itemize}}

\section{Honors and Awards}
\cventry{2020}{King Abdulaziz University}{University President's Prize for Scientific Excellence}{}{}{
\begin{itemize}
    \item[\ding{169}] Annual prize that is awarded for the graduate with the highest GPA.
\end{itemize} }
\cventry{2014, 2015}{Saudi Aramco and King Abdulaziz Center for World Culture}{Winner of iRead 2014 and 2015 competitions.}{}{}{
\begin{itemize}
    \item[\ding{169}] 10 winners are chosen among over 5000 candidates. 
    \item[\ding{169}] Wrote a book review and made a presentation in front of 300 people. 
\end{itemize} }

\section{Technical \& Computer Skills}
\cvitem{Operating Systems}{Linux, macOS, Windows.}
\cvitem{Programming Languages}{Python, C++, MATLAB.}
\cvitem{Others}{Latex, Quantum Espresso, git, EndNote, Microsoft Office.}

\section{Languages}
\cvitem{Arabic}{Native}
\cvitem{English}{Advanced, IELTS score of 7.5}
\cvitem{French}{A2/B1 Level}

\section{References}
\cvitem{Prof. Nicola Marzari}{Full Professor, Laboratory of theory and simulation of materials, EPFL. \newline
Email: nicola.marzari@epfl.ch
Phone: +41 21 693 11 29}

\cvitem{Prof. Udo Schwingeschlögl}{Professor, Applied Physics Chair, KAUST. \newline
Email: udo.schwingenschlogl@kaust.edu.sa}

\cvitem{Dr. Henric Wilkens}{Senior physicist in EP-ADE group at CERN. \newline
Email: Henric.Wilkens@cern.ch
Phone: +41 75 411 38 45}

\cvitem{Prof. Nuha Alhebshi}{Assistant Professor, Physics Department, King Abdulaziz University. \newline
Email: nalhebshi@kau.edu.sa}

\end{document}
